A GPU Implementation of Capon for an Active Sonar System

### 2012-05-04 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:04	15:04:34	(Fri 4.May)

\newpage
\section{Implementation}

@@

We have tested the \gls{CUDA} implementation of the \gls{MVDR} beamformer on experimental dat from $M=32$ element Kongsberg Maritime HISAS1030 sonar~\cite{Hansen2009}.

@@

\begin{figure}[!t]
\centering
\includegraphics{gfx/benchmark.png}
\caption{Capon benchmarks.}
\label{fig_sim}
\end{figure}

% A sidescan image of the 1500 dwt oil tanker wreck Holmengraa is shown in \Fig{holmengraa}. It is about 68\,m long and 9\,m wide, and lies on a slanted seabed at 77\,m depth~\cite{holmengraa}. The sidescan image was created using data from the HISAS 1030 sonar, which is rather unsuited for this purpose because of its large opening angle. This, and the fact that the wreck was imaged at a range of about 105\,m makes the image quality poor, but sufficient to compare our beamformers.

>>>>

\newpage
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{gfx/img_holmengraa.pdf}
\caption{HISAS sidescan sonar (SSS) image of the shipwreck Holmengraa.}\label{holmengraa}
\end{figure}

\section{Implementation}

@@

We have tested \gls{GPU} implementation of the \gls{MVDR} beamformer on experimental data from $M=32$ element Kongsberg Maritime HISAS1030 sonar~\cite{Hansen2009}. The sonar was attached to the HUGIN \gls{AUV}, and the imaged object was the 1500 dwt oil tanker wreck Holmengraa (fig. \ref{holmengraa}). Holmengraa is roughly 68\,m long and 9\,m wide, and lies on a slanted seabed at 77\,m depth.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{gfx/benchmark.pdf}
\caption{Capon benchmarks.}\label{benchmarks}
\end{figure}

% A sidescan image of the 1500 dwt oil tanker wreck Holmengraa is shown in \Fig{holmengraa}.  depth~\cite{holmengraa}. The sidescan image was created using data from the HISAS 1030 sonar, which is rather unsuited for this purpose because of its large opening angle. This, and the fact that the wreck was imaged at a range of about 105\,m makes the image quality poor, but sufficient to compare our beamformers.
